Sophize Markdown and Collaboration Interface

### 2021-07-11 paper1.tex
More improvements

In this paper, we first discuss the details of Sophize Markdown, an extension of Markdown language. It is convenient enough to be used for a casual discussion of mathematical ideas over the web. It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from a wide variety of sources, including formal languages. Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs. The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments. We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to develop our interface design. Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations. In fact, a large portion of the interface is designed specifically to overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}. We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.

@@

\subsection{Parser Extension: Tex Math}

\subsection{Parser Extension: Resource Links}

@@

The different resource link options provide different ways to embed a resource in the markdown. These are required to make it convenient for the content creators to provide a rich experience for their readers. The following are most commonly used:

@@

For propositions only. Adds a truth value icon indicating whether or not there is a proof available for the proposition. Clicking on the icon brings up the proof as a graph of arguments.

\paragraph{HIDE\_TVI}

The truth value icon is hidden.

@@

@@

Sophize collaboration interface is designed to allow multiple researchers to simultaneously discuss multiple approaches to solve the problem of interest. In open online collaborations, a lot of different ideas and approaches get introduced rapidly. Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that dissuades even the experts and the highly motivated. This work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects. We believe that the interface can aid many collaboration types - with few or many participants. We demonstrate the various features of this interface by incorporating actual data from a polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.

@@

Helping users make sense of the conversation and allowing them to get up to speed with existing conversation as quickly as possible is perhaps the most important requirement for managing online collaborations. To solve this problem, we need to organize the ideas that get tossed rapidly and summarize the progress. A reader should be able to quickly grasp the current progress, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.

Some of the other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):

@@

Even after the hierarchical division of comments, some pages can still have a large number of comments, which would be difficult to follow. To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far. For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste their time. Or to save time for future readers, they could summarize a sub-proof that was arrived at after dozens of comments.

@@

Comments in Sophize are numbered serially (starting with 1 for each collaboration), each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment). Comments in different projects can be references by providing the URI (\#URI/COMMENT\_NUMBER).

\subsection{Moderation Tools}

Sophize gives moderators usual tools like spam removal and fine-grained access control to manage participants. We also add a new feature where certain comments can be marked hidden. Often, threads of dozens of comments can be just noise because they were based on confused concepts or mistaken assumptions. Such comments should not be marked as spam. By marking such threads as `hidden', moderators can ensure that these are not shown by default. But any user can choose to see them if they wish to.

>>>>

In this paper, we first discuss the details of Sophize Markdown, an extension of Markdown language. It is convenient enough to be used for a casual discussion of mathematical ideas over the web. It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from a wide variety of sources, including formal languages. Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs. The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments. We studied the nature of collaboration on Polymath projects\cite{polymath_blog} - massively collaborative online mathematical projects to develop our interface design. Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations. In fact, a large portion of the interface is designed specifically to overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}. We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.

@@

\subsection{Embedding structured data}

@@

The different resource link options provide different ways to embed a resource in the markdown. These are required to make it convenient for the content creators to provide a rich experience to their readers. The following are most commonly used:

@@

For propositions only. Adds a truth value icon indicating whether or not there is a proof available for the proposition. Clicking on the icon brings up the proof as a graph of arguments. The HIDE\_TVI option makes sure that the truth value icon is always hidden.

@@

\subsection{\LaTeX\space Support}

@@

Sophize communication interface is designed to allow multiple researchers to collaboratively solve a problem. In such open online collaborations, a lot of different ideas and approaches get introduced rapidly. Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that dissuades even the experts and the highly motivated. We believe that we have created a novel interface that can significantly mitigate this problem. The work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects\cite{polymath_blog}. We believe that the interface can aid many collaboration types - with few or many participants. We demonstrate the various features of this interface by incorporating actual data from a polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.

@@

Helping users make sense of the conversation and allowing them to get up to speed with existing conversation as quickly as possible is perhaps the most important requirement for managing online collaborations. To solve this problem, we need to organize the ideas in an intuitive way  and summarize the progress. A reader should be able to quickly grasp the current progress, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.

Other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):

@@

Even after the hierarchical division of comments, some pages can still have a large number of comments, which would be difficult to follow. To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far. Comment summaries get embedded in the comment tree as a parent for comments they summarise. For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste their time. Or to save time for future readers, they could summarize a sub-proof that was arrived at after dozens of comments.

@@

Comments in Sophize are numbered serially (starting with 1 for each collaboration), each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment). Comments in an external project can be referenced by providing the project's URI (\#URI/COMMENT\_NUMBER).

Also, we make it extremely easy to extract terms, propositions and proofs from comments. These resources not only help in better understanding of the project, it also helps build Sophize's library.

\subsection{Reducing noise}

Sophize gives project moderators usual tools like spam removal and fine-grained access control to manage participants. We also add a new feature where certain comments can be marked hidden. Often, threads of dozens of comments can be just noise because they were based on confused concepts or mistaken assumptions. Such comments should not be marked as spam. By marking such threads as `hidden', moderators can ensure that these are not shown by default. But any user can see them if they wish to.
